%-------------------------
% Resume in LaTeX Template
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

%-------------------------
% Custom Commands - Fixed Jinja2 Issues

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}


%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Frederik Dahl Hansen } \\ \vspace{1pt}
    \small 416-200-0204 $|$
    \href{mailto:hansenf@sheridancollege.ca}{\underline{ hansenf@sheridancollege.ca }} $|$
    \href{https://linkedin.com/in/frederik-dahl-hansen}{\underline{linkedin.com/in/frederik-dahl-hansen}} $|$
    \href{https://github.com/dahlhansen}{\underline{github.com/dahlhansen}}
\end{center}

%-----------EDUCATION-----------

\section{Education}
\resumeSubHeadingListStart

    \resumeSubheading
        { Sheridan College }
        { Oakville, ON }
        { Bachelor of Computer Science (Mobile Computing) }
        { Jan. 2023 – Present }
    \resumeItemListStart
        
            \resumeItem{ GPA: 3.4 }
        
            \resumeItem{ Expected Graduation: 2026 }
        
            \resumeItem{ Seeking a 4-month internship for Summer 2025 }
        
    \resumeItemListEnd

\resumeSubHeadingListEnd


%-----------TECHNICAL SKILLS-----------

\section{Technical Skills}
\resumeSubHeadingListStart

    \item
    {\textbf{ Programming Languages}: Swift, Python, Java, C++, JavaScript, TypeScript, SQL, HTML/CSS, Bash}

    \item
    {\textbf{ Frameworks}: React, Node.js, ASP.NET, Flask, React Native, Angular, Vite, Tailwind}

    \item
    {\textbf{ Developer Tools}: Git, Firebase, Visual Studio Code, Xcode, IntelliJ, Postman, Swagger}

    \item
    {\textbf{ Databases}: PostgreSQL, MongoDB, Firebase Firestore}

    \item
    {\textbf{ Other Skills}: RESTful APIs, Agile Principles, SDLC, Web API Development, Shell Scripting, Unit Testing}

\resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart

\resumeProjectHeading
    {\textbf{ Rapid Resume } 
    \quad $|$ \quad 
    \emph{ Python, FastAPI, Swift, TeX }}{ 
    Feb. 2025 – Present }
    \resumeItemListStart
        
        \resumeItem{ Developing a streamlined resume-building application that enables users to quickly generate resumes. }
        
        \resumeItem{ Leveraging LaTeX for precise formatting, ensuring a polished and consistent resume layout. }
        
        \resumeItem{ Building a Swift-based frontend to provide an intuitive user experience for inputting personal and professional details. }
        
        \resumeItem{ Implementing FastAPI as the backend for efficient form handling and resume generation. }
        
        \resumeItem{ Allowing users to customize resume templates, adjusting layout and design elements dynamically. }
        
    \resumeItemListEnd

\resumeProjectHeading
    {\textbf{ Nova Weather } 
    \quad $|$ \quad 
    \emph{ Swift, Firebase Authentication, Gemini AI, API Integration }}{ 
    Sept. 2024 – Dec. 2024 }
    \resumeItemListStart
        
        \resumeItem{ Developed a Swift-based weather app with user creation, weather retrieval, and a favorite locations list. }
        
        \resumeItem{ Led UI/UX design, completing the layout in 4 weeks and planning a structured 6-week development phase. }
        
        \resumeItem{ Integrated Firebase Authentication for secure login, real-time validation, and encrypted data storage. }
        
        \resumeItem{ Optimized navigation and user flow, reducing browsing time by 30\%. }
        
    \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------EXPERIENCE-----------

\section{Experience}
\resumeSubHeadingListStart

    \resumeSubheading
        { Agent Services Coordinator }
        { Feb. 2024 – Present }
        { Sutton Group Quantum Realty Inc. }
        { Oakville, ON }
    \resumeItemListStart
        
            \resumeItem{ Manage the front desk efficiently, serving as the first point of contact for visitors, clients, and agents. }
        
            \resumeItem{ Implemented process improvements that enhanced front desk efficiency within five months. }
        
            \resumeItem{ Audited and corrected property listings, ensuring 100\% accuracy on real estate boards. }
        
            \resumeItem{ Utilized Microsoft Office applications to manage client records, update internal databases, and streamline administrative processes. }
        
            \resumeItem{ Assisted in onboarding new staff by providing training on internal systems and listing processes. }
        
    \resumeItemListEnd

\resumeSubHeadingListEnd


%-----------CO-CURRICULAR ACTIVITIES-----------

\section{Co-Curricular Activities}
\resumeSubHeadingListStart

    \resumeSubheading
        { President \& Founder }
        { Oct. 2024 – Present }
        { Sheridan Golf Club }
        { Oakville, ON }
    \resumeItemListStart
        
            \resumeItem{ Founded the club in 2024, collaborating with Sheridan’s student leadership to establish its mission. }
        
            \resumeItem{ Doubled membership within the first year through strategic outreach initiatives. }
        
            \resumeItem{ Led event planning efforts, fostering a strong networking community for golf enthusiasts. }
        
            \resumeItem{ Organized skill development sessions and events to enhance member engagement and participation. }
        
    \resumeItemListEnd

\resumeSubHeadingListEnd


\end{document}